---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Ivarima

<!-- badges: start -->
<!-- badges: end -->

This package implements a rule-based automated method for identifying the optimal intervention impact model for intervention ARIMA model.This method utilizes the impulse response function of the LTF model to infer the possible delay time and adopts the sequential Koyck model identification rules to guide the identification of decay pattern (h) and unpatterned spikes (r). An example describing how to install and use this package is described below. A more detailed tutorial, including the data analysis described in the paper, is also available with this package (pdf file)


## Installation

You can install the development version of Ivarima from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("XYanSerenity/Ivarima")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(Ivarima)

#library(Ivarima)
w0 <- 0.5
n <- 100
xt6 <- c(rep(0, 56), rep(1, 44))
e <- arima.sim(model = list(order = c(1, 0, 0), ar = 0.4, ma = NULL), n = 100, sd = 0.1)
xxt <- w0 * xt6
mu <- 4 + xxt
y <- mu + e
#model <- auto.ivarima(y = y, its_start = 51, LTFmaxk = 10)
#summary(model)
```
